Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-04-14 ms.tex
adding section about matrix matching conditions

TODO: Don't use s in these equations. Use damping rate omega here.
We employ an expansion in terms of spherical Bessel functions in $r$ and a Laplace expansion with the imaginary frequency variable $s=-i\omega$. The eigenvalues $s$ are real and negative for damped solutions to the time-dependent equation. The expansion for $J(r, \sigma, t)$ is

@@

\be
 \left( \frac{3k\phi}{c}i\omega  -   \kappa_n^2 \right) J(n,\sigma,\omega)  &+& \left( \frac{k}{\Delta} \right)^2 \frac{d^2J(n,\sigma,\omega)}{d\sigma^2} = \frac{2\kappa_n^2}{R} (-1) \frac{\sqrt{6}}{4\pi} \frac{kE}{\Delta^2} \frac{1}{4\pi} \delta(\sigma - \sigma_s).
\ee

@@

\be
\frac{\partial J_+}{\partial \sigma} - \frac{\partial J_-}{\partial \sigma} & = & 
- \frac{\sqrt{6}}{8} n^2 \frac{E}{kR^3}.
\ee

Two numerical integrations are performed inward from large $\pm \sigma$ to the source $
\sigma_s$. The starting values of J are set to be $J_1$ and $J_2$ for the rightward and leftward integrations, respectively. Choices of these starting values are adjusted to ensure that the matching conditions at the source are met.

Separating the real and imaginary parts of the solution $J = J_r + i J_i$, we have

@@

The starting conditions are $J_{1,r}$, $J_{1,i}$, $J_{2,r}$, $J_{2,i}$.
The rightgoing and leftgoing integrations then produce $J_{-,r}$, $J_{-,i}$, $J^\prime_{-,r}$, $J^\prime_{-,i}$,  $J_{+,r}$, $J_{+,i}$, $J^\prime_{+,r}$, $J^\prime_{+,i}$, where the prime means $\partial/\partial \sigma$. The matching conditions are then
\be
J_{-,r} & =& J_{+,r} \\
J_{-,i} & =& J_{+,i} \\
 J_{+,r}^\prime - J_{+,r}^\prime & = & 
- \frac{\sqrt{6}}{8} n^2 \frac{E}{kR^3} \\
J_{+,i}^\prime - J_{+,i}^\prime & = & 0.
\ee

>>>>

We employ an expansion in terms of spherical Bessel functions in $r$ and transform the time dependence into an imaginary frequency variable $\omega$. The eigenvalues $i\omega$ are real and positive for damped solutions to the time-dependent equation. The expansion for $J(r, \sigma, t)$ is

@@

\be
 \left( \frac{3k\phi}{c}i\omega  -   \kappa_n^2 \right) J(n,\sigma,\omega)  &+& \left( \frac{k}{\Delta} \right)^2 \frac{d^2J(n,\sigma,\omega)}{d\sigma^2} = -\frac{2\kappa_n^2}{R} \frac{\sqrt{6}}{4\pi} \frac{kE}{\Delta^2} \frac{1}{4\pi} \delta(\sigma - \sigma_s).
\ee

@@

\be
\frac{\partial J_+}{\partial \sigma} - \frac{\partial J_-}{\partial \sigma} & = & 
- \frac{\sqrt{6}}{8} n^2 \frac{E}{kR^3}
\ee

according to the differential equation. Two numerical integrations are performed inward from large $\pm \sigma$ to the source $\sigma_s$. The starting values of J are set to be $J_1$ and $J_2$ for the rightward and leftward integrations, respectively. Choices of these starting values are adjusted to ensure that the matching conditions at the source are met.

Separating the real and imaginary parts of the solution $J = J_r + i J_i$, the differential equation becomes

@@

The starting conditions are then $J_1 = J_{1,r} + iJ_{1,i}$ and $J_2 = J_{2,r}+iJ_{2,i}$.
The rightward and leftward integrations then produce $J_{-,r}$, $J_{-,i}$, $J^\prime_{-,r}$, $J^\prime_{-,i}$,  $J_{+,r}$, $J_{+,i}$, $J^\prime_{+,r}$, $J^\prime_{+,i}$, where a prime indicates a derivative $\partial/\partial \sigma$. The matching conditions at the source frequency $\sigma_s$ are then
\be
J_{-,r} & =& J_{+,r} \\
J_{-,i} & =& J_{+,i} \\
 J_{+,r}^\prime - J_{+,r}^\prime & = & 
- \frac{\sqrt{6}}{8} n^2 \frac{E}{kR^3} \\
J_{+,i}^\prime - J_{+,i}^\prime & = & 0.
\ee

The solutions at $\sigma=\sigma_s$ are parametrized as a linear combination of the real and imaginary parts of the starting conditions and are solved as a $4\times4$ matrix equation.
